PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Final edits to MHD section. All runs properly for NBR now.

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
    mhd.schizoaffective_disorder_numeric = NA
  )
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr mhd copy}
if(NBR == TRUE) {
  mhd.raw.id <- nbr.mhd.raw.id_renamed
}
```

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bingeeating_disorder_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "1" ~ 1)
    )
}

>>>>

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
  ) %>% 
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r nbr mhd copy}
if(NBR == TRUE) {
  mhd.raw.id <- nbr.mhd.raw.id
}
```

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bingeeating_disorder_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
    mhd.anorexia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
    mhd.atypical_anorexia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
    mhd.bulimia_nervosa =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
    mhd.bingeeating_disorder =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
    )
}
